Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-03-10 Manuscript/R&R/01-reviewer_1.Rmd
Rough draft of the response

__Response__:
\bigskip

@@

__Response__:
\bigskip

>>>>

__Response__: We thank the reviewer for the comment. We didn't perform the data processing step ourselves. We used the publicly available data that has been pre-processed. The data processing step is described in [TODO: add citation]. Meanwhile, we respectively argue that the small R2 is reasonable, as in many applications, genomics data can only accounts small amount of data variation. We think this example would be the case, as environmental factors (not accounted in these models) would be more substantial when explaining weight loss.
\bigskip

@@

__Response__: Thank you for the comment. The purpose of mentioning the other several priors in the previous manuscript is to describe the generalization of the proposed algorithms. In the updated manuscript, we move the subsection describing the other priors to the supporting information so that the readers can focus on understanding the proposed scalably model. We included an additional sentence in the discussion section. [TODO: list the sentence here].

Compared to other priors, the spike-and-slab double exponential prior provides three advantages. First of all, the spike-and-slab double exponential prior provides a locally adaptive shrinkage when estimating the coefficients. Hence, the smoothing functions can be estimated more accurately. Secondly, the spike-and-slab exponential prior encourages a sparse solution, making variable selection straight forward. Thirdly, the spike-and-slab double exponential prior motivates a scalable algorithm, the EM-CD algorithm, for model fitting, and hence is more feasible for high-dimensional data analysis.

We revised our method section to highlight these advantages, see Pxxx.

### 2022-03-10 Manuscript/R&R/02-reviewer_2.Rmd
Rough draft of the response

_Comments to the Authorss_

@@

@@

@@

__Response__: Thank you for the comment. We changed the prior distribution of the non-linear effects inclusion indicator to be $\gamma^\tp|\gamma, \theta \sim Bin(1, \gamma\theta)$ (See Equation ([TODO: add the equation number])), in comparison to $\gamma^\tp| \theta \sim Bin(1, \theta)$ previously. This prior formulation is motivated by effect forcing discussed in (Chipman, 2004). Now, the inclusion of the nonlinear effects is strictly dependent on the inclusion of the linear effects, and hence, reflects the hierarchy of bi-level selection. The modification of the prior doesn't complicate the model fitting algorithm. The $\gamma$ can be analytically integrated out of the density function (See Equation ([TODO: add the equation number]) and appendix) and requires minimum change of the proposed algorithms. In other words, the proposed model remain feasible for high-dimensional data analysis and retains the claimed computational advantages.

>>>>

_Comments to the Authors_

@@

__Response__: We thank the reviewer for the comment. The purpose of the reparameterization step is to factor the smoothing penalty matrix in the design matrix, such that the smoothing penalty is no long a function of the smoothing penalty matrix. In other words, the smoothing penalty changes from $\lambda \bs \beta^T \bs S \bs \beta$ to $\lambda \bs {\beta^*}^T \bs {\beta^*}$, where the $\bs \beta$ and $\bs \beta^*$ are the coefficients of the smoothing function before and after the reparameterization respectively. The spike-and-slab LASSO prior estimates whether to include the smoothing function and its appropriate smoothing parameter $\lambda$ with local adaptivity. This contrasts to previous methods that don't consider smoothing penalty at all or impose a uniform sparsity penalty upon uniform smoothing penalty, where both approaches tend to induce excessive shrinkage for the smoothing function.

In the updated manuscript, we clarify the utility of the reparmeterization step and emphasize how the smoothness of the additive function are properiately modeled. Please see the revision of the method section, highlighted in red.

@@

__Response__: Compared to other priors, the spike-and-slab double exponential prior provides three advantages. First of all, the spike-and-slab double exponential prior provides a locally adaptive shrinkage when estimating the coefficients. Hence, the smoothing functions can be estimated more accurately. Secondly, the spike-and-slab exponential prior encourages a sparse solution, making variable selection straight forward. Thirdly, the spike-and-slab double exponential prior motivates a scalable algorithm, the EM-CD algorithm, for model fitting, and hence is more feasible for high-dimensional data analysis.

We revised our method section to highlight these advantages, see Pxxx.
\bigskip

@@

__Response__: We thank the reviewer for the comment. We changed the prior distribution of the non-linear effects inclusion indicator to be $\gamma^\tp|\gamma, \theta \sim Bin(1, \gamma\theta)$ (See Equation ([TODO: add the equation number])), in comparison to $\gamma^\tp| \theta \sim Bin(1, \theta)$ previously. This prior formulation is motivated by effect forcing discussed in (Chipman, 2004). Now, the inclusion of the nonlinear effects is strictly dependent on the inclusion of the linear effects, and hence, reflects the hierarchy of bi-level selection. The modification of the prior doesn't complicate the model fitting algorithm. The $\gamma$ can be analytically integrated out of the density function (See Equation ([TODO: add the equation number]) and appendix) and requires minimum change of the proposed algorithms. In other words, the proposed model remain feasible for high-dimensional data analysis and retains the claimed computational advantages.

### 2022-03-10 Manuscript/R&R/03-reviewer_4.Rmd
Rough draft of the response

__Response__:
\bigskip

@@

__Response__:
\bigskip

@@

__Response__:
\bigskip

@@

__Response__:
\bigskip

@@

__Response__:
\bigskip

>>>>

__Response__: We thank the reviewer for the comment. We changed the prior distribution of the non-linear effects inclusion indicator to be $\gamma^\tp|\gamma, \theta \sim Bin(1, \gamma\theta)$ (See Equation ([TODO: add the equation number])), in comparison to $\gamma^\tp| \theta \sim Bin(1, \theta)$ previously. This prior formulation is motivated by effect forcing discussed in (Chipman, 2004). Now, the inclusion of the nonlinear effects is strictly dependent on the inclusion of the linear effects, and hence, reflects the hierarchy of bi-level selection. The modification of the prior doesn't complicate the model fitting algorithm. The $\gamma$ can be analytically integrated out of the density function (See Equation ([TODO: add the equation number]) and appendix) and requires minimum change of the proposed algorithms. In other words, the proposed model remain feasible for high-dimensional data analysis and retains the claimed computational advantages.
\bigskip

@@

__Response__: We thank the review for the comments. We added a new subsection discussing the function selection result from the simulation studies. The suggested metrics, including aaa, bbb, ccc are described for all models of comparisons. Lastly,the bi-level selection results are discussed too.
\bigskip

@@

__Response__: We thank the review for the comment. In the update manuscript, we add the suggested mdoel, spikeslabGAM, in the simulation study, where all the performance metrics and computation time are recorded and compared. We see that the proposed method still preserves the computation advantage over spikeSlabGAM, particularly in the high-dimensional cases.
\bigskip

@@

__Response__: We thank the reviewer for the comment. After careful deliberation, we decide to focusing an explaining the EM-CD method well. The inclusion of EM-IWLS would distract the reader from the main focus of manuscript, scalable model, good prediction and bi-level selection. We fully agree that the questions raised by the reviewer are very important and deserves careful discussion. Nevertheless, that would be out of the scope of the current work. We will dedicate another manuscript to detail many of the questions here, for example estimating effective degree of freedom, limiting distribution of the test statistics to the EM-IWLS method.

@@

__Response__: We thank the reviewer for the comment. We added more graphs displaying the effects of the significant effects.
\bigskip
